\chapter{Supplemental Material}
\section{Driver Survey}\label{appendix:survey}
\subsection{Basic Driving Information and Behavior}

\begin{enumerate}
    \item Which ride hailing platform companies did you work for in the last 30 days? (Select all that apply) 
    \begin{enumerate*}
        \item Grab 
        \item GoJek 
        \item Shopee
    \end{enumerate*}
    
    \item What type of vehicle do you use the most for work? 
    \begin{enumerate*}
        \item Car   
        \item Motorbike   
    \end{enumerate*}
    
    \item How did you acquire this vehicle? 
    \begin{enumerate}
        \item  I or a family member purchased it with full payment    
        \item  I or a family member purchased it on credit  
        \item I leased it through the ride-hailing platform  
        \item I leased it myself through a third party \item Others (please specify) 
    \end{enumerate}
    
    \item Did you drive for a taxi company in the last 30 days, e.g. for bluebird?
    \begin{enumerate*}
        \item  Yes
        \item  No
    \end{enumerate*}
    
    \item Did you work in any other jobs in addition to either ride-hailing and/or taxi driving in the last 30 days?  
    \begin{enumerate*}
        \item  Yes (please specify job type) 
        \item  No
    \end{enumerate*}
    
    \item Did this job give you more money per hour than money for an hour you are on bid? 
    \begin{enumerate*}
        \item  Yes
        \item  No
    \end{enumerate*}
    
    \item Do you like this job more or less than working for Grab/GoJek/Shopee? 
    \begin{enumerate*}
        \item   Yes
        \item   No
        \item Indifferent
    \end{enumerate*}
    
    \item What job did you have before starting as an ojol?
    \begin{enumerate*}
        \item  Opang  
        \item  Other
        \item Ojol is my first job
    \end{enumerate*}
    
    \item Did this job give you more money per hour than money for an hour you are on bid? 
    \begin{enumerate*}
        \item   Yes
        \item   No
    \end{enumerate*}
    
    \item Why did you change jobs? (Select all that apply)
    \begin{enumerate}
        \item Better pay  
        \item Lost my previous job  
        \item More flexible hours
        \item My friends were joining ojol
        \item I like this job better
        \item More respected/higher status as an ojol
        \item Other (Please specify)
    \end{enumerate}
    
    \item Where do you prefer to wait when not on an order (most frequently)? 
    \begin{enumerate}
        \item  Wait in the area where last ride/order ended 
        \item  Drive to nearest hangout/resting spots with other drivers 
        \item Driver to high demand areas even if I have to drive there  
        \item Others (please specify)  
    \end{enumerate}
    
    \item When do you usually stop working (most frequently)? 
    \begin{enumerate}
        \item  When I reach a certain income
        \item  When I get enough points/tupo  
        \item  At a set time I set for myself  
        \item  When I get tired  
        \item  Others (please specify)  
    \end{enumerate}
\end{enumerate}
    
\subsection{Multihoming Behavior}
\subsubsection{For Non-Multi-Homers}

\begin{enumerate}
\setcounter{enumi}{12}
    \item Why do you not use multiple platforms and only use one platform? Check whether you agree with the following statements. 
    \begin{enumerate}
        \item I have enough work on one so do not need to work for both (Disagree/Agree)
        \item  I fear retaliation by the platform (Disagree/Agree)
        \item I understand one system much better than the other (Disagree/Agree)
        \item I feel loyal to my platform (Disagree/Agree)
        \item I want to maintain my ranking on one of the platform (Disagree/Agree)	 
        \item I don’t like the other platform (Disagree/Agree)
        \item My friends/community are on this platform (Disagree/Agree)
        \item I want to concentrate/focus on one platform for better performance (Disagree/Agree)
    \end{enumerate}
    
    \item Would the following factors be important in your decision to start working for multiple platforms at the same time? 
    \begin{enumerate}
        \item  Higher bonus on the other platform (Yes/No)
        \item  Higher income on the other platform (Yes/No)
        \item  No penalty for multihoming (Yes/No)
        \item My friends/community began to multihome (Yes/No)
        \item More orders/demand on the other platform (Yes/No)
        \item Understanding the other system better (Yes/No)
    \end{enumerate}
    
    \item If you were to leave your current platform and ONLY WORK for the other platform, would the following factors be important in the decision to switch?
    \begin{enumerate}
        \item  Higher bonus on the other platform (Yes/No)
        \item  Higher Income on the other platform (Yes/No)
        \item More orders/demand on the other platform (Yes/No)	 
        \item All your friends/community shifting to the other platform (Yes/No)
        \item Understanding the other system better (Yes/No)
        \item None of these will make me change to the other platform and leave my current application (Yes/No)
    \end{enumerate}
    
    \item Anything else we should know about why you decided to not use multiple platforms?
\end{enumerate}

\subsubsection{For Multi-Homers}

\begin{enumerate}
\setcounter{enumi}{16}
    \item How do you usually switch between multiple companies? 
    \begin{enumerate}
        \item Have multiple phones open at the same time  
        \item I block times, i.e. have one company open on my phone for each time period 
        \item Have multiple apps running on the same phone throughout the day
        \item Only check the other company when I don’t get orders for some time 
        \item Others (please specify)  
    \end{enumerate}
    
    \item What percentage of your working day do you have multiple phones open at the same time? (0 - 100)
    
    \item Were the following factors important in your decision to start working for multiple platforms?
    \begin{enumerate}
        \item  Getting a higher bonus on one of the platforms (Yes/No)
        \item  Making more income on one of the platform (Yes/No)
        \item Knowing there is no penalty for multihoming (Yes/No)
        \item More demand on one of the platforms (Yes/No)
    \end{enumerate}
    
    \item Any other reasons you started working for multiple platforms?
    
    \item When working for multiple platforms, are you worried about the following?  
    \begin{enumerate}
        \item  I fear being penalized by platforms for multihoming (Yes/No)
        \item  I understand one system much better than the other (Yes/No)
        \item I feel disloyal to the company working for both (Yes/No)	
        \item I feel disloyal to the my friends/community working for both (Yes/No)
        \item Working for both platforms is distracting/I can't focus on one (Yes/No)
        \item It is difficult to maintain ranking on one platform (Yes/No)
    \end{enumerate}
    
    \item What would make you work EXCLUSIVELY for a platform and not multihome?  (Select all that apply)
    \begin{enumerate}
        \item Higher bonus on this platform  
        \item Higher Income on this platform  
        \item More orders/demand on this platform 
        \item No penalty to multihoming  
        \item All my friends/community shifting to this platform  
        \item Others (please specify)  
        \item None of these will make me change to working for only one platform  
    \end{enumerate}
    
     \item Anything else we should know about your decision to use multiple platforms?
\end{enumerate}

\subsection{Driving Activities}

\paragraph{Note.} This set of questions is also asked for Grab and GoJek if respondents select Grab or GoJek in Question 1. We only show questions for Shopee in this section, which has one additional Shopee-specific question compared to Grab and GoJek.


\noindent
\paragraph{For the next set of questions think about your activity only for Shopee for the last 30 days}
\begin{enumerate}
\setcounter{enumi}{23}
    \item Which Shopee service did you take most orders from?
    \begin{enumerate*}
        \item  Food  
        \item  Other
        \item  No specialization
    \end{enumerate*} 
    
    \item (Shopee-specific question) What has changed when Shopee appears?
    \begin{enumerate}
        \item I drive less for GoJek  
        \item I drive less for Grab  
        \item I drive more for GoJek
        \item I drive more for Grab  
        \item No changes
    \end{enumerate}
    
    \item What type of area do you spend most of your online search time for Shopee?
    \begin{enumerate*}
        \item  Central areas  
        \item  Outskirts  
    \end{enumerate*}
    
    \item Out of the following, Which area do you spend most of your online/search time for Shopee in? 
    \begin{enumerate*}
        \item North Jakarta  
        \item South Jakarta  
        \item East Jakarta  
        \item West Jakarta  
        \item Central Jakarta  
        \item Other area (Bodetabek) 
    \end{enumerate*}
    
    \item What days a week do you usually drive for Shopee at least one trip? (Select all that apply)  
    \begin{enumerate*}
        \item  Monday
        \item  Tuesday 
        \item Wednesday
        \item Thursday
        \item Friday
        \item Saturday
        \item Sunday
    \end{enumerate*}
    
    \item How many hours do you typically work for Shopee on these days?
    \begin{enumerate}
        \item Weekdays (0 - 24)
        \item Weekends (0 - 24)
    \end{enumerate}
    
    \item For the last two weeks: What has been your average daily salary from Shopee on weekdays? (in Rp)
    
    \item For the last two weeks: What has been your average daily salary from Shopee on Saturdays and Sundays? (in Rp)
    
    \item How many kilometers have you driven on average daily for Shopee when on bid [If more than 300, move slide to maximum value]? (0 - 300 KM)
    
    \item How satisfied are you with Shopee's:
    \begin{enumerate}
        \item Bonus Scheme (1 - 5)
        \item Daily Income you make on the platform (1 - 5)
        \item Matching system (1 - 5)
        \item Responsiveness to driver complaints/problems (1 - 5)
    \end{enumerate}
    
    \item When working for Shopee, approximately how many days do you hit your bonus? 
    \begin{enumerate*}
        \item  All the time  
        \item  Around half the time  
        \item  Less than half the time  
    \end{enumerate*}
\end{enumerate}

\subsection{Sociodemographic Information}

\begin{enumerate}
\setcounter{enumi}{34}
    \item What is your age? 
    \begin{enumerate*}
        \item Under 20  
        \item 20 - 29
        \item 30 - 39
        \item 40 - 49
        \item Above 50
    \end{enumerate*}
    
    \item What is your gender?
    \begin{enumerate*}
        \item Male
        \item Female
        \item Non-binary / third gender  
        \item Prefer not to answer  
    \end{enumerate*}
    
    \item What is the highest degree you obtained? 
    \begin{enumerate*}
        \item SD
        \item SMP
        \item SMA
        \item D3
        \item S1 or higher
        \item None of the above
    \end{enumerate*}
    
    \item Is Grab/GoJek your main source of income?
    \begin{enumerate*}
        \item  Yes
        \item  No
    \end{enumerate*}
    
    \item How many people does your income support (not including yourself)? (0 - 10)
    
    \item Approximately how much do you spend on food each week? (in Rp)
    
    \item How much do you spend on rent each week? (in Rp)
    
    \item What is your kecamatan?
    
    \item What is your kelurahan?
\end{enumerate}

\section{Decision Environment for Reinforcement Learning Agents}
Here, we describe the observed state and action for the Reinforcement Learning challenge, compare \cite{Xie2020}. 
\subsection{Dispatch Challenge}
The order dispatch, a matching challenge, observes as an observable state for each incoming order and each idle driver in the platform during each time step
\begin{itemize}
	\item The estimated distance from driver to order
	\item The origin and destination of the order
	\item The estimated order start and completion time assuming the order was matched to the driver
	\item The reward units as an earnings proxy for the driver.
\end{itemize}
The state of the system contains all driver's locations at each time.


\subsection{Repositioning Challenge}
The repositioning challenge observes as an observable state for each driver in a \emph{targeted} group of drivers that is idle for at least 5 minutes and each time step at which repositioning is possible a coarse location of the driver on a coarse grid of Chengdu.